Logarithmic Space Verifiers on NP-complete

### 2019-10-31 doc/manuscript.tex
Fixed the doc content

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L. In this way, we obtain that L = NL and P = NP cannot be both true or false at the same time and thus, the complexity class L is not equal to NP.
\end{abstract}

@@

In previous years there has been great interest in the verification or checking of computations \cite{LIP90}. Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}. Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}. In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}. More about probabilistic logarithmic space verifiers have been shown on a technique of Lipton \cite{LIP90}. In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $L$ versus $NP$.

@@

\begin{theorem}
\label{argument}
If the Hypothesis \ref{hypothesis} is true, then $L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
\end{theorem}

@@

Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}. If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}. Since we already obtained that $P = NP$ under the assumption of $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$. Hence, if $P \neq NP$, then $L = NL$ by contraposition \cite{Pap03}. Consequently, $L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
\end{proof}

@@

\begin{theorem}
$L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
\end{theorem}

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L. In this way, we obtain that L = NL and P = NP cannot be both false at the same time.
\end{abstract}

@@

In previous years there has been great interest in the verification or checking of computations \cite{LIP90}. Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}. Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}. In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}. More about probabilistic logarithmic space verifiers have been shown on a technique of Lipton \cite{LIP90}. In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which impact into one of the most important open problems in computer science, that is $P$ versus $NP$.

@@

\begin{theorem}
\label{argument}
If the Hypothesis \ref{hypothesis} is true, then $L = NL$ and $P = NP$ cannot be both false at the same time.
\end{theorem}

@@

Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}. If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}. Since we already obtained that $P = NP$ under the assumption of $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$. Hence, if $P \neq NP$, then $L = NL$ by contraposition \cite{Pap03}. Consequently, $L = NL$ and $P = NP$ cannot be both false at the same time.
\end{proof}

@@

\begin{theorem}
$L = NL$ and $P = NP$ cannot be both false at the same time.
\end{theorem}
